Inference methods comparison for the simplified Naomi model using the Kolmogorov-Smirnov test statistic

### 2023-07-21 src/docs_paper/appendix.Rmd
Add plot with ESS against KS result for TMB and PCA-AGHQ #55

>>>>

```{r ks-ess, fig.cap="The ESS was negatively correlated with KS test statistic for both TMB and PCA-AGHQ. This could be explained in two ways. First, harder to sample parameters could be more difficult to estimate with approximate methods. Second, as more effective samples are collected, the NUTS posterior could become closer to the approximate posteriors."}
knitr::include_graphics("depends/ks-ess.png")
```

### 2023-07-21 src/naomi-simple_ks/ks.Rmd
Add plot with ESS against KS result for TMB and PCA-AGHQ #55

```{r}
rhats <- bayesplot::rhat(tmbstan$mcmc$stanfit)
ess_ratio <- bayesplot::neff_ratio(tmbstan$mcmc$stanfit)
niter <- 4 * tmbstan_details$niter / tmbstan_details$nthin
ess <- ess_ratio * niter

ks_df %>%
  filter(type != "Hyper") %>%
  left_join(data.frame(ess) %>%
    tibble::rownames_to_column("par"),
  ) %>%
  ggplot(aes(x = ess, y = ks)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", color = "#56B4E9") +
    facet_grid(~ method) +
    theme_minimal() +
    labs(x = "ESS", y = "KS(method, tmbstan)")
```

>>>>

```{r}
rhats <- bayesplot::rhat(tmbstan$mcmc$stanfit)
ess_ratio <- bayesplot::neff_ratio(tmbstan$mcmc$stanfit)
niter <- 0.5 * 4 * tmbstan_details$niter / tmbstan_details$nthin
ess <- ess_ratio * niter

fct_reorg <- function(fac, ...) {
  fct_recode(fct_relevel(fac, ...), ...)
}

ks_df %>%
  filter(type != "Hyper") %>%
  mutate(method = fct_reorg(method, "TMB" = "TMB", "PCA-AGHQ" = "aghq")) %>%
  left_join(data.frame(ess) %>%
    tibble::rownames_to_column("par"),
  ) %>%
  ggplot(aes(x = ess, y = ks)) +
    geom_point(shape = 1, alpha = 0.5) +
    geom_smooth(method = "lm", color = "#56B4E9", fullrange = TRUE) +
    stat_poly_eq(use_label("eq"), label.x.npc = "right") +
    stat_poly_eq(label.y = 0.9, label.x.npc = "right") +
    scale_x_continuous(limits = c(0, NA)) +
    facet_grid(~ method) +
    theme_minimal() +
    labs(x = "ESS", y = "KS(method, NUTS)")

ggsave("ks-ess.png", h = 4, w = 6.25)
```
